---
title: "Exploratory analysis"
author: "Izolda Motiejauskyte"
date: "12/1/2019"
output: 
  html_document: 
    fig_height: 8
    fig_width: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo=FALSE, message=FALSE}
#install.packages("RCurl")
#install.packages("zip")
#install.packages("ggplot2")
#install.packages("ggpubr")
#install.packages("dplyr")
#install.packages("forcats")
#install.packages('hrbrthemes')
#install.packages("gridExtra")
#install.packages("plyr")

library(ggplot2)
library(ggpubr)
library(plyr)
library(dplyr)
library(zip)
library(RCurl)
library(forcats)
library(hrbrthemes)
library(gridExtra)

########################################
########## DOWNLOADING DATA#############
########################################

link <- "https://offshoreleaks-data.icij.org/offshoreleaks/csv/csv_panama_papers.2018-02-14.zip#_ga=2.124687823.439045129.1575110567-884049020.1575110567"
#_ga=2.103652677.439045129.1575110567-884049020.1575110567
  #as.character(commandArgs(trailingOnly=TRUE)[2])
#create temp file
dir.create(temp <- tempfile())
#download zip file from given URL
download.file(link, paste0(temp, '/PZUURT.zip'), mode = 'wb', exdir = temp)
#unzip file
unzip(paste0(temp, '/PZUURT.zip'), exdir = temp)
#read tables from unziped file
root_folder <- paste0(temp)
## create list of csv files in unziped folder
filelist <- list.files(path = root_folder, pattern = '*.csv', recursive = TRUE)
##clean names for data frames
filenames <- basename(filelist)
table_name <- sub("nodes.","",sub("[a-z]*_[a-z]*.","",sub(".csv", "", filelist)))
##read data frames
table_path <- paste(root_folder, filelist,sep='\\')
for(i in 1:length(table_name)){
  filepath <- table_path[i]
  assign(table_name[i], read.table(filepath,header=TRUE,sep=',',fill=T))
}
```



# Summary

Report is splited into three parts:
1. Stand alone data sets analysis;
2. Combined information analysis;
3. Swedbank home markets (include four countries - Sweden, Lithuania, Latvia, Estonia) analysis.

Due to consistency between different data leaks we investigate only nodes that can be found in all four possible data sets. Analysis include information about entity, officer, intermediary and address nodes.   

# Stand alone data sets analysis

## Entity

### Entity count by registration country and jurisdiction country 

```{r echo=FALSE,message=FALSE}
#creating Other category for country and jurisdiction of entity (leaving only top 20 countries and top 20 jurisdictions)
entity$group_countries<- fct_lump(entity$countries,n=20)
entity$group_jurisdictions <- fct_lump(entity$jurisdiction_description,n=20)

# frequency tables for country and jurisdiction of entity
ent_country_freq <- entity %>%
  group_by(group_countries) %>%
  dplyr::summarise(counts = n())

ent_jurisdiction_freq <- entity %>%
  group_by(group_jurisdictions) %>%
  dplyr::summarise(counts = n())

# histograms of country and jurisdiction of entity
ent_count_hist <- ggplot(ent_country_freq, aes(x = reorder(group_countries,-counts), counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Entity country") + ylab("Frequency")


ent_jur_hist <- ggplot(ent_jurisdiction_freq, aes(x = reorder(group_jurisdictions,-counts), counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Entity jurisdiction") + ylab("Frequency")

#ploting histograms in one plot
ggarrange(ent_count_hist,ent_jur_hist,
          labels = c("", ""),
          ncol = 2, nrow = 1)
```

### Entity registration country and jurisdiction country heatmap

```{r echo=FALSE, message=FALSE}
#creating entity country and jurisdiction heatmap
ent_count_juris_freq <- data.frame(table(entity$group_countries,entity$group_jurisdictions))

 ggplot(ent_count_juris_freq, aes(Var1, Var2, fill= Freq)) + 
  geom_tile() +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") + 
   theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   xlab("Entity country") + ylab("Entity jurisdiction")
```

### Entity incorporation time series and entity status at the moment

```{r echo=FALSE, message=FALSE}
#creating entity incorporation timeseries graph and status of entities at the moment
entity$incorporation_date <- as.Date(entity$incorporation_date,format="%d-%b-%Y")
ent_incorp_date_freq <- data.frame(table(entity$incorporation_date))
ent_incorp_date_freq$Var1 <- as.Date(ent_incorp_date_freq$Var1,format="%Y-%m-%d")
ggplot(data = ent_incorp_date_freq, aes(x = Var1, y = Freq))+
  geom_line(color = "#00AFBB", size = 1)+
  xlab("Incorporation Date") + ylab("# of Entities")
```

```{r echo=FALSE, message=FALSE}
ent_status_freq <- data.frame(table(entity$status))
ggplot(ent_status_freq, aes(x = reorder(Var1,-Freq), Freq)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = Freq), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Entity Status") + ylab("Frequency")
```

## Intermediary

### Intermediary count by country and intermediary status

```{r echo=FALSE, message=FALSE}
#creating intermediary freaquency by country and status of intermediary
intermediary$group_countries<- fct_lump(intermediary$countries,n=20)
ggplot(intermediary, aes(group_countries))+geom_bar(aes(fill = status))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Intermediary Country") + ylab("Frequency")
```

## Officer

### Officer count by country

```{r echo=FALSE, message=FALSE}
officer$group_countries<- fct_lump(officer$countries,n=20)
off_country_freq <- officer %>%
  group_by(group_countries) %>%
  dplyr::summarise(counts = n())

ggplot(off_country_freq, aes(x = reorder(group_countries,-counts), counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Officer Country") + ylab("Frequency")
```

## Address

### Address count by address country 

```{r echo=FALSE, message=FALSE}
# creating address frequency by country
address$group_countries<- fct_lump(address$countries,n=20)
add_country_freq <- address %>%
  group_by(group_countries) %>%
  dplyr::summarise(counts = n())

ggplot(add_country_freq, aes(x = reorder(group_countries,-counts), counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Adress Country") + ylab("Frequency")
```

# Combined information analysis

```{r echo=FALSE, message=FALSE}
#creating subset of edges by typpe
edges_address <- edges[edges$TYPE=='registered_address',]
edges_officer <- edges[edges$TYPE=='officer_of',]
edges_intermediary <- edges[edges$TYPE=='intermediary_of',]

#merging address and edges about address information

address_information <- merge(x=edges_address,y=address,by.x="END_ID",by.y="node_id",all.x=TRUE, suffixes = c("",".ed_add"))
address_information <- address_information[,names(address_information) %in% c("START_ID","link","address","countries")]

#merging officer and edges about officer information
officer_information <- merge(x=officer,y=address_information,by.x="node_id",by.y="START_ID",all.x=TRUE, suffixes = c("",".add_off"))
officer_information <- merge(x=edges_officer,y=officer_information,by.x="START_ID",by.y="node_id",all.x=TRUE, suffixes = c("",".ed_off"))
officer_information <- officer_information[,names(officer_information) %in% c("END_ID","link.ed_off","name","countries","address")]

#merging intermediary and edges about intermediary information
intermediary_information <- merge(x=intermediary,y=officer_information,by.x="node_id",by.y="END_ID",all.x=TRUE, suffixes = c("",".off_off"))
intermediary_information <- merge(x=edges_intermediary,y=intermediary_information,by.x="START_ID",by.y="node_id",all.x=TRUE, suffixes = c("",".ed_int"))
intermediary_information <- intermediary_information[,names(intermediary_information) %in% c("END_ID","link.ed_int","name","countries","status","name.off_off")]

#creating one data set where entity information is base
entity_full <- entity[,-c(13:17)]

#adding address information
entity_full <- merge(x=entity_full,y=address_information,by.x="node_id",by.y="START_ID",all.x=TRUE, suffixes = c("",".ed_add"))
names(entity_full)[names(entity_full) == 'link'] <- 'address_type'
names(entity_full)[names(entity_full) == 'countries.ed_add'] <- 'address_country'

#adding officer information
entity_full <- merge(x=entity_full,y=officer_information,by.x="node_id",by.y="END_ID",all.x=TRUE, suffixes = c("",".ed_off"))
names(entity_full)[names(entity_full) == 'link.ed_off'] <- 'officer_type'
names(entity_full)[names(entity_full) == 'countries.ed_off'] <- 'officer_country'
names(entity_full)[names(entity_full) == 'name.ed_off'] <- 'officer_name'
names(entity_full)[names(entity_full) == 'address.ed_off'] <- 'officer_address'

#adding intermediary information
entity_full <- merge(x=entity_full,y=intermediary_information,by.x="node_id",by.y="END_ID",all.x=TRUE, suffixes = c("",".ed_int"))
names(entity_full)[names(entity_full) == 'link.ed_int'] <- 'intermediary_type'
names(entity_full)[names(entity_full) == 'countries.ed_int'] <- 'intermediary_country'
names(entity_full)[names(entity_full) == 'name.ed_int'] <- 'intermediary_name'
names(entity_full)[names(entity_full) == 'status.ed_int'] <- 'intermediary_status'
names(entity_full)[names(entity_full) == 'name.off_off'] <- 'intermediary_officer'
```

### Frequency graph about officer having entities in domestic/foreign countries

```{r echo=FALSE, message=FALSE}
#Creating function that identifies domestic/foreign country

group_f <- function(a,b){
  if (is.na(b)) { 
      "Missing"
  } else if (b==a) {
      "Domestic country"
  } else {
      "Foreign country"
  }
}

group_country_f<-Vectorize(group_f)

#filtering data set to have only rows where information about officer exists
cleaned_officer_country <- entity_full[is.null(entity_full$officer_country)==FALSE & is.na(entity_full$officer_country)==FALSE&entity_full$officer_country!="",]

#identifying if entity country is domestic/foreign based on officer country
cleaned_officer_country $officer_entity_group <- group_country_f(cleaned_officer_country$officer_country,cleaned_officer_country$countries)

#creating frequency graph about officer having entities in domestic/foreign countries
cleaned_officer_country $group_officer_country<- fct_lump(cleaned_officer_country $officer_country,n=20)
ggplot(cleaned_officer_country , aes(group_officer_country))+geom_bar(aes(fill = officer_entity_group))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Officer country") + ylab("Frequency")
```

### Officer country and Entity country heatmap

```{r echo=FALSE, message=FALSE}
#creating officer country and entity country heatmap
cleaned_officer_country $group_entity_country<- fct_lump(cleaned_officer_country $countries,n=20)
ent_count_off_count_freq <- data.frame(table(cleaned_officer_country$group_entity_country,cleaned_officer_country$group_officer_country))

ggplot(ent_count_off_count_freq, aes(Var1, Var2, fill= Freq)) + 
  geom_tile() +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Entity country") + ylab("Officer country")
```

### Frequency graph about intermediary working with entities in domestic/foreign countries

```{r echo=FALSE, message=FALSE}
#cleaning data to have only rows where information about intermediary exists
cleaned_intermediary_country <- entity_full[is.null(entity_full$intermediary_country)==FALSE & is.na(entity_full$intermediary_country)==FALSE&entity_full$intermediary_country!="",]

#identifying if intermediary works within domestic/foreign country
cleaned_intermediary_country$intermediary_entity_group <- group_country_f(cleaned_intermediary_country$intermediary_country,cleaned_intermediary_country$countries)

#creating frequency graph about intermediary working with entities in domestic/foreign countries
cleaned_intermediary_country $group_intermediary_country<- fct_lump(cleaned_intermediary_country $intermediary_country,n=20)
ggplot(cleaned_intermediary_country , aes(group_intermediary_country))+geom_bar(aes(fill = intermediary_entity_group))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Intermediary country") + ylab("Frequency")
```

### Intermediary country and entity country heatmap

```{r echo=FALSE, message=FALSE}
# creating intermediary country and entity country heatmap
cleaned_intermediary_country $group_entity_country<- fct_lump(cleaned_intermediary_country $countries,n=20)
ent_count_int_count_freq <- data.frame(table(cleaned_intermediary_country$group_entity_country,cleaned_intermediary_country$group_intermediary_country))

ggplot(ent_count_int_count_freq, aes(Var1, Var2, fill= Freq)) + 
  geom_tile() +
  scale_fill_continuous(high = "#132B43", low = "#56B1F7") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Entity country") + ylab("Intermediary country")
```

### List of entity countries and number of different intermediary countries working with
```{r echo=FALSE, message=FALSE}
#create list of entity countries and number of different countries of intermediaries working with
ddply(cleaned_intermediary_country,~group_entity_country,summarise,number_of_distinct_intermediary_country=length(unique(group_intermediary_country)))

```

# Swedbank home markets

## Entity count by registration country and jurisdiction country

```{r echo=FALSE, message=FALSE}
#filtering home markets
entityH <- entity[entity$countries %in% c("Lithuania","Latvia","Estonia","Sweden"),]


#creating Other category for country and jurisdiction of entityH (leaving only top 20 countries and top 20 jurisdictions)
entityH$group_countries<- fct_lump(entityH$countries,n=20)
entityH$group_jurisdictions <- fct_lump(entityH$jurisdiction_description,n=20)

# frequency tables for country and jurisdiction of entityH
ent_country_freq_H <- entityH %>%
  group_by(group_countries) %>%
  dplyr::summarise(counts = n())

ent_jurisdiction_freq_H <- entityH %>%
  group_by(group_jurisdictions) %>%
  dplyr::summarise(counts = n())

# histograms of country and jurisdiction of entityH
ent_count_hist_H <- ggplot(ent_country_freq_H, aes(x = reorder(group_countries,-counts), counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Entity Country") + ylab("Frequency")


ent_jur_hist_H <- ggplot(ent_jurisdiction_freq_H, aes(x = reorder(group_jurisdictions,-counts), counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Entity Jurisdiction") + ylab("Frequency")

#ploting histograms in one plot
ggarrange(ent_count_hist_H,ent_jur_hist_H,
          labels = c("", ""),
          ncol = 2, nrow = 1)
```

### Entity incorporation time series and entity status at the moment
```{r echo=FALSE, message=FALSE}
#creating entity incorporation timeseries graph and status of entities at the moment
entityH$incorporation_date <- as.Date(entityH$incorporation_date,format="%d-%b-%Y")
ent_incorp_date_freq_H <- data.frame(table(entityH$incorporation_date))
ent_incorp_date_freq_H$Var1 <- as.Date(ent_incorp_date_freq_H$Var1,format="%Y-%m-%d")
ent_time_series_H <- ggplot(data = ent_incorp_date_freq_H, aes(x = Var1, y = Freq))+
  geom_line(color = "#00AFBB", size = 1)+
  xlab("Incorporation Date") + ylab("# of Entities")

ent_status_freq_H <- data.frame(table(entityH$status))
ent_status_hist_H <- ggplot(ent_status_freq_H, aes(x = reorder(Var1,-Freq), Freq)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = Freq), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Entity Status") + ylab("Frequency")

ggarrange(ent_time_series_H,ent_status_hist_H,
          labels = c("", ""),
          ncol = 1, nrow = 2)
```

### Intermediary count by country and intermediary status
```{r echo=FALSE, message=FALSE}
#filtering home markets
intermediaryH <- intermediary[intermediary$countries %in% c("Lithuania","Latvia","Estonia","Sweden"),]


#creating intermediary freaquency by country and status of intermediary
intermediaryH$group_countries<- fct_lump(intermediaryH$countries,n=20)
ggplot(intermediaryH, aes(group_countries))+geom_bar(aes(fill = status))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Intermediary Country") + ylab("Frequency")
```

### Officer count by country
```{r echo=FALSE, message=FALSE}
#filtering home markets
officerH <- officer[officer$countries %in% c("Lithuania","Latvia","Estonia","Sweden"),]

#creating officer frequency by country
officerH$group_countries<- fct_lump(officerH$countries,n=20)
off_country_freq_H <- officerH %>%
  group_by(group_countries) %>%
  dplyr::summarise(counts = n())

ggplot(off_country_freq_H, aes(x = reorder(group_countries,-counts), counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Officer Country") + ylab("Frequency")
```

### Address count by address country 
```{r echo=FALSE, message=FALSE}
addressH <- address[address$countries %in% c("Lithuania","Latvia","Estonia","Sweden"),]

#creating address frequency by country
addressH$group_countries<- fct_lump(addressH$countries,n=20)
add_country_freq_H <- addressH %>%
  group_by(group_countries) %>%
  dplyr::summarise(counts = n())

ggplot(add_country_freq_H, aes(x = reorder(group_countries,-counts), counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  theme_pubclean()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  xlab("Adress Country") + ylab("Frequency")
```